Members

### 2025-08-12 members.qmd
minor edit, 250812GH

**[Willi Sauerbrei](https://www.uniklinik-freiburg.de/english/imbi/mitarbeiter.html?imbiuser=wfs) (chair)**: Institute for Medical Biometry and Medical Informatics, Medical Center - University of Freiburg, Germany

>>>>

**[Willi Sauerbrei](https://www.uniklinik-freiburg.de/imbi-en/employees.html?imbiuser=wfs) (chair)**: Institute for Medical Biometry and Medical Informatics, Medical Center - University of Freiburg, Germany
